### 2017-05-10 capacited-vehicle-routing/article/article.tex
Added results and fixed minor bug

% !TEX root = ./article.tex

\documentclass[spanish]{article}

\usepackage{mystyle}
\usepackage{myvars}
\usepackage{mylinearprogramming}

%-----------------------------

\begin{document}

	\maketitle % Insert title

	\thispagestyle{fancy} % All pages have headers and footers

%-----------------------------
%	ABSTRACT
%-----------------------------

	\begin{abstract}
		\noindent [TODO ]
	\end{abstract}

%-----------------------------
%	TEXT
%-----------------------------

	\section{Introducción}
	\label{sec:intro}

		\paragraph{}
		[TODO ]

		\subsection{Modelización Exacta}

			\paragraph{}
			[TODO ]

		\subsection{Heurística de Clarke y Wright}

			\paragraph{}
			[TODO ]

	\section{Resolución de Problemas}

		\subsection{Residuos}

			\paragraph{}
			[TODO ]

			\begin{table}[H]
				\centering
				\begin{tabu}{ | c | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Método & \bfseries Vehículos  & \bfseries Distancia & \bfseries Caminos
					\csvreader[head to column names]{../results/csv/residuos.csv}{}
					{\\\hline\method&\vehicles&\distance&\path}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-residuos}
			\end{table}

		\subsection{Gasóleos}

			\paragraph{}
			[TODO ]

			\begin{table}[H]
				\centering
				\begin{tabu}{ | c | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Método & \bfseries Vehículos  & \bfseries Distancia & \bfseries Caminos
					\csvreader[head to column names]{../results/csv/gasoleos.csv}{}
					{\\\hline\method&\vehicles&\distance&\path}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-gasoleos}
			\end{table}

		\subsection{E021-04m}

			\paragraph{}
			[TODO ]

			\begin{figure}[h]
				\centering
				\begin{subfigure}{.4\textwidth}
					\centering
					\includegraphics[width=\linewidth]{E021-04m-exact}
					\caption{Solución \emph{Exacta}}
				\end{subfigure} \
				\begin{subfigure}{.4\textwidth}
					\centering
					\includegraphics[width=\linewidth]{E021-04m-clarke-wright}
					\caption{Solución \emph{Clarke y Wright}}
				\end{subfigure}
				\caption{[TODO ]}
				\label{fig:sol-e021-04m}
			\end{figure}

			\begin{table}[H]
				\centering
				\begin{tabu}{ | c | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Método & \bfseries Vehículos  & \bfseries Distancia & \bfseries Caminos
					\csvreader[head to column names]{../results/csv/e021-04m.csv}{}
					{\\\hline\method&\vehicles&\distance&\path}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-e021-04m}
			\end{table}

		\subsection{E026-08m}

			\paragraph{}
			[TODO ]

			\begin{figure}[h]
				\centering
				\begin{subfigure}{.4\textwidth}
					\centering
					\includegraphics[width=\linewidth]{E026-08m-exact}
					\caption{Solución \emph{Exacta}}
				\end{subfigure} \
				\begin{subfigure}{.4\textwidth}
					\centering
					\includegraphics[width=\linewidth]{E026-08m-clarke-wright}
					\caption{Solución \emph{Clarke y Wright}}
				\end{subfigure}
				\caption{[TODO ]}
				\label{fig:sol-e026-08m}
			\end{figure}

			\begin{table}[H]
				\centering
				\begin{tabu}{ | c | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Método & \bfseries Vehículos  & \bfseries Distancia & \bfseries Caminos
					\csvreader[head to column names]{../results/csv/e026-08m.csv}{}
					{\\\hline\method&\vehicles&\distance&\path}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-e026-08m}
			\end{table}

		\subsection{E051-05e}

			\paragraph{}
			[TODO ]

			\begin{figure}[h]
				\centering
				\begin{subfigure}{.4\textwidth}
					\centering
					\includegraphics[width=\linewidth]{e051-05e-exact}
					\caption{Solución \emph{Exacta}}
				\end{subfigure} \
				\begin{subfigure}{.4\textwidth}
					\centering
					\includegraphics[width=\linewidth]{e051-05e-clarke-wright}
					\caption{Solución \emph{Clarke y Wright}}
				\end{subfigure}
				\caption{[TODO ]}
				\label{fig:sol-e051-05e}
			\end{figure}

			\begin{table}[H]
				\centering
				\begin{tabu}{ | c | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Método & \bfseries Vehículos  & \bfseries Distancia & \bfseries Caminos
					\csvreader[head to column names]{../results/csv/e051-05e.csv}{}
					{\\\hline\method&\vehicles&\distance&\path}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-e051-05e}
			\end{table}

		\subsection{E076-10e}

			\paragraph{}
			[TODO ]

			\begin{figure}[h]
				\centering
				\begin{subfigure}{.4\textwidth}
					\centering
					\includegraphics[width=\linewidth]{E076-10e-exact}
					\caption{Solución \emph{Exacta}}
				\end{subfigure} \
				\begin{subfigure}{.4\textwidth}
					\centering
					\includegraphics[width=\linewidth]{E076-10e-clarke-wright}
					\caption{Solución \emph{Clarke y Wright}}
				\end{subfigure}
				\caption{[TODO ]}
				\label{fig:sol-e076-10e}
			\end{figure}

			\begin{table}[H]
				\centering
				\begin{tabu}{ | c | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Método & \bfseries Vehículos  & \bfseries Distancia & \bfseries Caminos
					\csvreader[head to column names]{../results/csv/e076-10e.csv}{}
					{\\\hline\method&\vehicles&\distance&\path}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-e076-10e}
			\end{table}

%-----------------------------
%	BIBLIOGRAPHY
%-----------------------------
	\nocite{subject:mio}
	\nocite{garciparedes:mosel-examples}
	\bibliographystyle{acm}
  \bibliography{bib/misc}

\end{document}