### 2017-05-24 scheduling/article/article.tex
Added results

% !TEX root = ./article.tex

\documentclass[spanish]{article}

\usepackage{mystyle}
\usepackage{myvars}
\usepackage{mylinearprogramming}

%-----------------------------

\begin{document}

	\maketitle % Insert title

	\thispagestyle{fancy} % All pages have headers and footers

%-----------------------------
%	ABSTRACT
%-----------------------------

	\begin{abstract}
		\noindent [TODO ]
	\end{abstract}

%-----------------------------
%	TEXT
%-----------------------------

	\section{Introducción}
	\label{sec:intro}

		\paragraph{}
		[TODO ]

	\section{Resolución de Problemas}
	\label{sec:problems}

		\subsection{\texttt{sched\_10\_1}}

			\paragraph{}
			[TODO ]

			\begin{table}[h]
				\centering
				\begin{tabu}{ | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Modelo & \bfseries Retraso & \bfseries Programación
					\csvreader[head to column names]{../results/csv/sched_10_1.csv}{}
					{\\\hline\model&\delay&\schedule}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-sched_10_1}
			\end{table}

		\subsection{\texttt{sched\_20\_1}}

			\paragraph{}
			[TODO ]

			\begin{table}[h]
				\centering
				\begin{tabu}{ | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Modelo & \bfseries Retraso & \bfseries Programación
					\csvreader[head to column names]{../results/csv/sched_20_1.csv}{}
					{\\\hline\model&\delay&\schedule}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-sched_20_1}
			\end{table}

		\subsection{\texttt{sched\_30\_1}}

			\paragraph{}
			[TODO ]

			\begin{table}[h]
				\centering
				\begin{tabu}{ | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Modelo & \bfseries Retraso & \bfseries Programación
					\csvreader[head to column names]{../results/csv/sched_30_1.csv}{}
					{\\\hline\model&\delay&\schedule}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-sched_30_1}
			\end{table}

		\subsection{\texttt{sched\_40\_1}}

			\paragraph{}
			[TODO ]

			\begin{table}[h]
				\centering
				\begin{tabu}{ | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Modelo & \bfseries Retraso & \bfseries Programación
					\csvreader[head to column names]{../results/csv/sched_40_1.csv}{}
					{\\\hline\model&\delay&\schedule}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-sched_40_1}
			\end{table}

		\subsection{\texttt{sched\_100\_1}}

			\paragraph{}
			[TODO ]

			\begin{table}[h]
				\centering
				\begin{tabu}{ | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Modelo & \bfseries Retraso & \bfseries Programación
					\csvreader[head to column names]{../results/csv/sched_100_1.csv}{}
					{\\\hline\model&\delay&\schedule}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-sched_100_1}
			\end{table}

		\subsection{\texttt{sched\_200\_1}}

			\paragraph{}
			[TODO ]

			\begin{table}[h]
				\centering
				\begin{tabu}{ | c | c | p{.58\linewidth} |}
					\hline
					\bfseries Modelo & \bfseries Retraso & \bfseries Programación
					\csvreader[head to column names]{../results/csv/sched_200_1.csv}{}
					{\\\hline\model&\delay&\schedule}
					\\\hline
				\end{tabu}
				\caption{[TODO ]}
				\label{table:sol-sched_200_1}
			\end{table}

%-----------------------------
%	BIBLIOGRAPHY
%-----------------------------
	\nocite{subject:mio}
	\nocite{garciparedes:mosel-examples}
	\bibliographystyle{acm}
  \bibliography{bib/misc}

\end{document}